The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-08 main.tex
Fixed typo in DH acknowledgements

\section{Introduction} \label{sec:intro}
All astronomical research makes use of software in some way.
Astronomy as a field has thus long supported the development of software tools
for astronomical tasks, such as scripts that enable individual scientific
research, software packages for small collaborations, and data reduction
pipelines for survey operations.
Some software packages are or were supported by large institutions and are
intended for a wide range of users.
These packages therefore typically provide some level of documentation and user
support or training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
For both packages meant for wider distribution and for scripts specific to
particular research projects, a library that addresses common astronomical tasks
simplifies the software development process.
The users of such a library then also benefit from a community and ecosystem
built around a shared foundation.
The \astropy project has grown to become this community for \python astronomy
software, and the \astropypkg core package a feature-rich \python library.

@@

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example}
\caption{%
    An example showing different modes of convolution available in the \python
    ecosystem.  Each red $x$ signifies a pixel that is set to \texttt{NaN} in the
    original data (a).  If the data are convolved with a Gaussian kernel on a
    $9\times 9$ grid using
    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the
    \texttt{NaN}s are set to zero first: the originally \texttt{NaN} regions are
    depressed relative to their surroundings.  Finally, panel (d) shows
    \astropypkg's convolution behavior, where the missing pixels are replaced
    with values interpolated from their surroundings using the convolution
    kernel.
    \label{fig:convolution-example}
}
\end{figure}

>>>>

\section{Introduction} \label{sec:intro}
All modern astronomical research makes use of software in some way.
Astronomy as a field has thus long supported the development of software tools
for astronomical tasks, such as scripts that enable individual scientific
research, software packages for small collaborations, and data reduction
pipelines for survey operations.
Some software packages are or were supported by large institutions and are
intended for a wide range of users.
These packages therefore typically provide some level of documentation and user
support or training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
For both packages meant for wider distribution and for scripts specific to
particular research projects, a library that addresses common astronomical tasks
simplifies the software development process.
The users of such a library then also benefit from a community and ecosystem
built around a shared foundation.
The \astropy project has grown to become this community for \python astronomy
software, and the \astropypkg core package a feature-rich \python library.

@@

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example}
\caption{%
    An example showing different modes of convolution available in the \python
    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the
    original data (a).  If the data are convolved with a Gaussian kernel on a
    $9\times 9$ grid using
    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the
    \texttt{NaN}s are set to zero first: the originally \texttt{NaN} regions are
    depressed relative to their surroundings.  Finally, panel (d) shows
    \astropypkg's convolution behavior, where the missing pixels are replaced
    with values interpolated from their surroundings using the convolution
    kernel.
    \label{fig:convolution-example}
}
\end{figure}
